---
title: "Text_mining"
author: "Yingjie"
date: "01/23/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---


  This script aims to use human intelligence to evaluate the accuracy of the text mining results. 
  For details, please refer to [this report](https://drive.google.com/file/d/1EHUV6Jc3N4A-IshKU4dbxtIqlfj50mzi/view)
  
  
# Directories and packages

```{r include=FALSE}
### To clear your environment
remove(list = ls())


# directories
dir.this <- "./docs/accuracy_evaluation/"
dir.data <- paste0(dir.this, "data/")
dir.figures <- dir.this

# load packages
library(dplyr)
library(readxl)
library(writexl)

library(tidyverse) # piping and wrangling
library(ggplot2)
library(ggpubr)
```



# Data

  We validated the accuracy by conducting three round of test. For each round, we asked 
  four experts to identify if the machine-coded results are correct or not. 
  
  The data are save in XLSX files under each round's folder. 
  
  ```
  
  ./docs/accuracy_evaluation/
      |
      |__ data/
      |    |
      |    |__ task1_R1_done/
      |    |
      |    |__ task1_R2_done/
      |    |
      |    |__ task1_R3_done/
      |
      |
      |__ (results and figures)
      
  ```
  
## 1. Clean data from each round

  First, we need to 
    - read in and clean four coders' data
    - calculate the accuracy based on each coder's evaluation 
    - check alignment across coders 
    - save result in xlsx for visualization 
  
  Please modify `nth_round` and run all the code in this section 
  (i.e., Section ## 1. Clean data from each round) before running code in the 2nd section
  for visualization. In this case, you will need to run code in section 1 for three times. 
  
```{r - read and clean}
getwd()


## choose the round number and run all code in section 1.
nth_round <- 1
# nth_round <- 2
# nth_round <- 3


## list data from this round of evaluation -----------------------------------------------
dir.task1 <- paste0(dir.data, "task1_R", nth_round, "_done")
dir.task1
f.ls <- list.files(path = dir.task1, pattern = "task1_", full.names = T, recursive = T)
f.ls
## test line
# f    <- "./Data/data_TextMining/coded_validation_coder/planB_done/task1/task1_YL.xlsx"


## read in all the XLSX ------------------------------------------------------------------
ds <- data.frame()
for (f in f.ls) {
  coder <- basename(f) %>% gsub("task1_|\\.xlsx", "", .)
  coder
  d <- readxl::read_excel(path = f) %>%
    dplyr::mutate(coder = coder, index = as.numeric(row.names(.)))
  ds <- rbind(ds, d)
}

unique(ds$correct_or_not)
unique(ds$coder)


## unify the checking result to "0, 1, NA" only ------------------------------------------
ds0 <- ds %>%
  dplyr::mutate(coder = gsub(pattern = ".*_", "", coder)) %>% ## clean coder name
  dplyr::mutate(correct_or_not = gsub(pattern = "\\*", "", correct_or_not)) %>% ## clean coder's response
  dplyr::mutate(correct = case_when(
    correct_or_not == "1" ~ 1,
    correct_or_not == "0" ~ 0,
    is.na(correct_or_not) ~ NA_real_,
    grepl("^Y", correct_or_not) ~ 1,
    TRUE ~ 0
  )) %>%
  dplyr::select(coder, correct, correct_or_not, everything())


ds1 <- ds0 %>%
  arrange(correct_or_not)



## to check the alignment across coders --------------------------------------------------
ds2 <- ds1 %>%
  dplyr::select(coder, correct, company, index) %>%
  ## only analyze rows being checked
  # dplyr::filter(!is.na(correct)) %>%
  spread(key = coder, value = correct) %>%
  dplyr::mutate(
    same12 = ifelse(MC == VF, 1, 0),
    same13 = ifelse(MC == YL, 1, 0),
    same14 = ifelse(MC == YZ, 1, 0),
    same23 = ifelse(VF == YL, 1, 0),
    same24 = ifelse(VF == YZ, 1, 0),
    same34 = ifelse(YL == YZ, 1, 0),
    same3 = ifelse(MC == YL & YZ == YL, 1, 0),
    same4 = ifelse(MC == YL & YZ == YL & VF == YL, 1, 0)
  ) %>%
  as.data.frame()
```



```{r - accuracy}
names(ds2)

### The accuracy of our SDGdetector judged by SDG experts
ds_accuracy <- ds2 %>%
  dplyr::select(company, index, MC, VF, YL, YZ) %>%
  gather(key = "coder", value = "value", 3:ncol(.)) %>%
  dplyr::group_by(coder) %>%
  dplyr::summarise(accuracy = sum(value, na.rm = T) / nrow(ds2)) %>%
  dplyr::mutate(id = row.names(.)) %>%
  dplyr::select(id, everything())
ds_accuracy


### test code
# (sum(ds2$MC, na.rm = T)/nrow(ds2)) %>%
#   scales::percent() %>%
#   cat('accuracy by MC:', .)
```




```{r - alignment across coders}
names(ds2)

### The inter-expert reliability
ds_intercoder <- ds2 %>%
  dplyr::select(company, index, same12, same13, same14, same23, same24, same34) %>%
  gather(key = "pair", value = "value", 3:ncol(.)) %>%
  dplyr::group_by(pair) %>%
  dplyr::summarise(alignment = sum(value, na.rm = T) / nrow(ds2))

ds_intercoder
```



```{r - save result in xlsx}
## save to XLSX for easy read
f <- paste0(dirname(dir.task1), "/", "results_accuracy_", basename(dir.task1), ".xlsx")
f
writexl::write_xlsx(ds_accuracy, path = f)

f <- paste0(dirname(dir.task1), "/", "results_intercoder_", basename(dir.task1), ".xlsx")
f
writexl::write_xlsx(ds_intercoder, path = f)
```



## 2. Visulzation of the results

```{r - read in results}
## for accuracy
ind <- "results_accuracy_"
fs <- list.files(path = dirname(dir.task1), pattern = ind, full.names = T)
# f <- fs[1]
dfs_acc <- data.frame()

for (f in fs) {
  # print(f)
  round_id <- f %>%
    basename(.) %>%
    gsub(ind, "", .) %>%
    gsub("task1_|_done.xlsx", "", .)
  # print(round_id)

  acc <- readxl::read_excel(f) %>%
    dplyr::mutate(round_id = round_id)
  dfs_acc <- rbind(dfs_acc, acc)
}



## for inter-coder
ind <- "results_intercoder_"
fs <- list.files(path = dirname(dir.task1), pattern = ind, full.names = T)
# f <- fs[1]
dfs_int <- data.frame()

for (f in fs) {
  # print(f)
  round_id <- f %>%
    basename(.) %>%
    gsub(ind, "", .) %>%
    gsub("task1_|_done.xlsx", "", .)
  # print(round_id)

  int <- readxl::read_excel(f) %>%
    dplyr::mutate(round_id = round_id)
  dfs_int <- rbind(dfs_int, int)
}
```




```{r - plot accuracy}
## plot ----------------------------------------------------------------------------------

mean(dfs_acc$accuracy)
fun_mean <- function(x) {
  return(data.frame(y = mean(x), label = round(mean(x, na.rm = T), digits = 2)))
}

p1 <- dfs_acc %>%
  ggplot(aes(x = 1, y = accuracy)) +
  geom_boxplot(fill = "gray", show.legend = F, varwidth = .5) + # , fill = round_id
  stat_summary(fun = mean, geom = "point", shape = 15, size = 3, alpha = 0.6, color = "red", fill = "red") +
  stat_summary(fun.data = fun_mean, geom = "text", vjust = .5, hjust = -0.2, color = "red") +
  scale_y_continuous(limits = c(0.7, .85)) +
  geom_jitter(color = "black", shape = 1, size = 2, alpha = 0.6, width = .05) +
  xlab("Overall") +
  ylab("Accuracy") +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(colour = "transparent"),
    axis.ticks = element_blank(),
    legend.position = "none"
  )
p2 <- dfs_acc %>%
  ggplot(aes(x = round_id, y = accuracy)) + # , fill = round_id
  geom_boxplot(alpha = .8) + #
  scale_y_continuous(limits = c(0.7, .85)) +
  geom_jitter(color = "black", shape = 1, size = 2, alpha = 0.6, width = .05) +
  xlab("Each Round of Inspection") +
  ylab("") +
  theme_bw() +
  theme(legend.position = "none")
p <- ggarrange(p1, p2, widths = c(1, 3))

fname <- paste0(dir.figures, "Inspection_Accuracy.png")
fname
ggsave(fname, plot = p, width = 6.5, height = 3.2, units = "in", dpi = 300)
```


```{r - plot inter-coder}
p3 <- dfs_int %>%
  ggplot(aes(x = 1, y = alignment)) +
  geom_boxplot(fill = "gray", show.legend = F, varwidth = .5) + # , fill = round_id
  stat_summary(fun = mean, geom = "point", shape = 15, size = 3, alpha = 0.6, color = "red", fill = "red") +
  stat_summary(fun.data = fun_mean, geom = "text", vjust = .7, hjust = -0.3, color = "red") +
  scale_y_continuous(limits = c(0.7, .9)) +
  geom_jitter(color = "black", shape = 1, size = 2, alpha = 0.6, width = .05) +
  xlab("Overall") +
  ylab("Inter-expert Reliability") +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(colour = "transparent"),
    axis.ticks = element_blank(),
    legend.position = "none"
  )


p4 <- dfs_int %>%
  ggplot(aes(x = round_id, y = alignment)) + # , fill = round_id
  geom_boxplot(alpha = .8) + #
  scale_y_continuous(limits = c(0.7, .9)) +
  geom_jitter(color = "black", shape = 1, size = 2, alpha = 0.6, width = .05) +
  xlab("Each Round of Inspection") +
  ylab("") +
  theme_bw() +
  theme(legend.position = "none")
p <- ggarrange(p3, p4, widths = c(1, 3))

fname <- paste0(dir.figures, "Inspection_InterExpert.png")
fname
ggsave(fname, plot = p, width = 6.5, height = 3.2, units = "in", dpi = 300)
```


 
